Model of a DSL for finite state machines

### 2014-12-29 docs/fsml/paper.tex
Working on the syntax chapter of the slbook

\title{Another DSL primer}

@@

\noindent
\textbf{Acknowledgement}: {\small This document and the underlying
  development are parts of a broader effort on language modeling and
  software language engineering---joint work with \emph{Anya Helene
    Bagge}, University of Bergen. Helpful interaction with and
  feedback by Andrei Varanovich, University of Koblenz-Landau, is also
  gratefully acknowledged.}

@@

0.00004 as of 2 October 2014.

@@

\noindent
\textbf{Repository location of document}:

\url{https://github.com/slebok/slepro/tree/master/docs/fsml}.
\end{abstract}

@@

The FSML development is part of the \slepro{} project. All software
artifacts of this document and all support infrastructure is available
through the repository of the project:

\begin{center}
\url{https://github.com/slebok/slepro}
\end{center}

>>>>

\title{Model of a DSL for finite state machines}

@@

\noindent
\textbf{Acknowledgement}: {\small This document and the underlying
  development are parts of a broader effort on language modeling and
  software language engineering. Collaboration with and feedback by
  Anya Helene Bagge (University of Bergen) and Andrei Varanovich
  (University of Koblenz-Landau) are gratefully acknowledged.}

@@

0.1 as of 11 November 2014.

@@

\noindent
\textbf{Website of this document}:

\smallskip

\url{http://softlang.uni-koblenz.de/fsml/}

\smallskip

\noindent
The page also links to supplementary repository locations. In
particular, the model (code) of this document as well as alternative
implementations of FSML are linked. The FSML model is maintained as
part of the \slepro{} project: \url{https://github.com/slebok/slepro}
\end{abstract}

@@
